Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-03-29 analyses/reproduce_analyses.Rmd
created orthogonal polynomials and adjusted downstream code to match names appropriately. let's see if it works.

         # transform and scale traits to approximate multivariate normal assumption
         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))

@@

```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
```

```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
```

@@

```{r Food-web model, cache=TRUE}
foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Linear food-web model, cache=TRUE}
linear_foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Bootstrap linear food-web model, cache=TRUE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

# Fit linear model with only chamber diameter 
biased_foodweb_model <- glmer(
  gall_survival ~ -1 + Foodweb + 
    Foodweb:sc.Diam + 
    (1|Genotype/Plant_Position/Gall_Number),
  data = biased_foodweb_df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

@@

```{r biased foodweb table, echo=FALSE}
# Print table
biased_foodweb_confint %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
```

@@

```{r Food-web alpha coefficients}
foodweb_bind <- bind_cols(
  as_tibble(boot_linear_foodweb_model$t),
  select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
)

# Adjust coefficients with chamber diameter
foodweb_adj_Diam <- foodweb_bind %>%
  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],
         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_alphas <- foodweb_adj_Diam %>%
  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
  select(-FoodwebSimple, -FoodwebComplex) %>% # translated into (Intercept) terms
  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_alphas <- foodweb_alphas %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
```

@@

# Plot linear trait-fitness relationaships
plot_foodweb_linear_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot quadratic trait-fitness relationships
plot_foodweb_quadratic_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot correlational trait-fitness relationaships
plot_foodweb_correlational_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

@@

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_grads <- bind_cols(foodweb_complex_raw_gradients, foodweb_simple_raw_gradients) %>%
  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_grads <- foodweb_grads %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
```

@@

```{r Curvature, echo=FALSE}
# Calculate curvatures for complex food web
foodweb_complex_raw_curvs <- foodweb_complex_raw_gradients %>%
  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:I(sc.Diam^2)` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.Diam`,
         `FoodwebComplex:C.Clutch` = `FoodwebComplex:I(sc.log.Clutch^2)` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.log.Clutch`,
         `FoodwebComplex:C.Pref` = `FoodwebComplex:I(sc.sqrt.Pref^2)` - `FoodwebComplex:sc.sqrt.Pref`*`FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.log.Clutch`,
         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.sqrt.Pref`)

# Calculate curvatures for simple food web
foodweb_simple_raw_curvs <- foodweb_simple_raw_gradients %>%
  transmute(`FoodwebSimple:C.Diam` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.Diam`,
         `FoodwebSimple:C.Clutch` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.log.Clutch`,
         `FoodwebSimple:C.Pref` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebSimple:sc.sqrt.Pref`*`FoodwebSimple:sc.sqrt.Pref`,
         `FoodwebSimple:C.Diam:Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.log.Clutch`,
         `FoodwebSimple:C.Diam:Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.sqrt.Pref`,
         `FoodwebSimple:C.Clutch:Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.sqrt.Pref`)

>>>>

         # transform and scale traits to approximate multivariate normal assumption
         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))),
         # create orthogonal polynomial terms
         sc.Diam.1 = poly(sc.Diam, 2)[ ,1],
         sc.Diam.2 = poly(sc.Diam, 2)[ ,2],
         sc.log.Clutch.1 = poly(sc.log.Clutch, 2)[ ,1],
         sc.log.Clutch.2 = poly(sc.log.Clutch, 2)[ ,1],
         sc.sqrt.Pref.1 = poly(sc.sqrt.Pref, 2)[ ,1],
         sc.sqrt.Pref.2 = poly(sc.sqrt.Pref, 2)[ ,2]) 
```

@@

```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam.1, sc.log.Clutch.1, sc.sqrt.Pref.1), univariatePlot = "histogram")
```

```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam.1, sc.log.Clutch.1, sc.sqrt.Pref.1), multivariatePlot = "qq")
```

@@

```{r Food-web model, cache=TRUE}
foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb:(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Linear food-web model, cache=TRUE, eval=FALSE}
linear_foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Bootstrap linear food-web model, cache=TRUE, eval=FALSE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

# Fit linear model with only chamber diameter 
biased_foodweb_model <- glmer(
  gall_survival ~ -1 + Foodweb + 
    Foodweb:sc.Diam.1 + 
    (1|Genotype/Plant_Position/Gall_Number),
  data = biased_foodweb_df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

@@

```{r biased foodweb table, echo=FALSE}
# Print table
biased_foodweb_confint %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term %in% c("FoodwebComplex:sc.Diam.1","FoodwebSimple:sc.Diam.1")) %>%
  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
```

@@

```{r Food-web alpha coefficients}
foodweb_bind <- as_tibble(boot_foodweb_model$t) #bind_cols(
  #as_tibble(boot_linear_foodweb_model$t),
  #select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:sc.Diam.2`:`FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1`) # only retain nonlinear coefficients from full model
#)

# Adjust coefficients with chamber diameter
foodweb_adj_Diam <- foodweb_bind %>%
  mutate(`FoodwebComplex:sc.Diam.1` = `FoodwebComplex:sc.Diam.1` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam.1"],
         `FoodwebSimple:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam.1"])

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_alphas <- foodweb_adj_Diam %>%
  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
  select(-FoodwebSimple, -FoodwebComplex) %>% # translated into (Intercept) terms
  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
         `FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_alphas <- foodweb_alphas %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
                                   ifelse(grepl("\\.2", .$term)==TRUE, "Quadratic",
                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
```

@@

# Plot linear trait-fitness relationaships
plot_foodweb_linear_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
  ggplot(., aes(x=term)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot quadratic trait-fitness relationships
plot_foodweb_quadratic_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

# Plot correlational trait-fitness relationaships
plot_foodweb_correlational_coefs <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

@@

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_grads <- bind_cols(foodweb_complex_raw_gradients, foodweb_simple_raw_gradients) %>%
  mutate(`FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_grads <- foodweb_grads %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         gradient_type = ifelse(grepl("\\.2", .$term)==TRUE, "Quadratic",
                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
```

@@

```{r Curvature, echo=FALSE}
# Calculate curvatures for complex food web
foodweb_complex_raw_curvs <- foodweb_complex_raw_gradients %>%
  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:sc.Diam.2` - `FoodwebComplex:sc.Diam.1`*`FoodwebComplex:sc.Diam.1`,
         `FoodwebComplex:C.Clutch` = `FoodwebComplex:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.1`*`FoodwebComplex:sc.log.Clutch.1`,
         `FoodwebComplex:C.Pref` = `FoodwebComplex:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.1`*`FoodwebComplex:sc.sqrt.Pref.1`,
         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1`*`FoodwebComplex:sc.log.Clutch.1`,
         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1`*`FoodwebComplex:sc.sqrt.Pref.1`,
         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1`*`FoodwebComplex:sc.sqrt.Pref.1`)

# Calculate curvatures for simple food web
foodweb_simple_raw_curvs <- foodweb_simple_raw_gradients %>%
  transmute(`FoodwebSimple:C.Diam` = `FoodwebSimple:sc.Diam.2` - `FoodwebSimple:sc.Diam.1`*`FoodwebSimple:sc.Diam.1`,
         `FoodwebSimple:C.Clutch` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebSimple:sc.log.Clutch.1`*`FoodwebSimple:sc.log.Clutch.1`,
         `FoodwebSimple:C.Pref` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebSimple:sc.sqrt.Pref.1`*`FoodwebSimple:sc.sqrt.Pref.1`,
         `FoodwebSimple:C.Diam:Clutch` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebSimple:sc.Diam.1`*`FoodwebSimple:sc.log.Clutch.1`,
         `FoodwebSimple:C.Diam:Pref` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebSimple:sc.Diam.1`*`FoodwebSimple:sc.sqrt.Pref.1`,
         `FoodwebSimple:C.Clutch:Pref` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebSimple:sc.log.Clutch.1`*`FoodwebSimple:sc.sqrt.Pref.1`)
